---
title: "SEV_PlantBiomassRegressions_RoundOne"
author: "AJ"
date: '`r Sys.time()`'
output: html_document
---

##Background
Several long-term studies at the Sevilleta LTER measure net primary production (NPP) across ecosystems and treatments. Net primary production is a fundamental ecological variable that quantifies rates of carbon consumption and fixation. Estimates of NPP are important in understanding energy flow at a community level as well as spatial and temporal responses to a range of ecological processes. Above-ground net primary production (ANPP) is the change in plant biomass, including loss to death and decomposition, over a given period of time. To measure this change, vegetation variables, including species composition and the cover and height of individuals, are sampled up to three times yearly (winter, spring, and fall) at permanent plots within a study site. Sevilleta LTER dataset 157 includes cover, height, and dry biomass measurements obtained through destructive harvesting. These species are always harvested from habitat comparable to the plots in which they were recorded.

##Purpose
The following R code utilizes volume (cover x height) and weight data from Sev dataset 157 to create regressions which can be used to estimate seasonal biomass for plant species across the Sevilleta.

```{r load.packages, include=FALSE}
# Load R packages which will be used in this script
library(ggplot2)
library(lubridate)
library(plyr)
library(reshape2)
library(gridExtra)
library(cowplot)
library(knitr)
library(markdown)
library(xtable)
library(zoo)
library(tidyr)
library(stats)
library(car)
library(nlme)
library(visreg)
```

### Output
This script will output a report for each species for which we have destructive harvest biomass data. This report will include sample size, information about where and when samples come from, p-values for each significant interaction term in a model, and figures visually describing these interactions. 
Predictor variables  include:  
-individual plant volume (height*cover)
-site at which plant occurs
-season during which plant was observed
-treatment (burned or unburned)
-year during which destructive harvest sample was collected  

Separately, a spreadsheet including linear model slopes and p-values for each pairwise comparison of the above the terms will be created. 

Next steps include investigating how burn effects change over time, which sites are functionally similar, which seasons are functionally similar, and what climate variables drive interannual variation in allometries for each species.

### Step 1: Preparing the data
SEV dataset 157 (version 20161218) is used here.
```{r, include=F}
# Read in SEV 157 and format columns
dest.harv.raw <- read.csv("/Users/alesia/Documents/Project_SevPublicPlantRCode/sev157_nppweight_20161218.csv", strip.white=T)

# Look at the data
summary(dest.harv.raw)

# Modify column names
names(dest.harv.raw)[names(dest.harv.raw) == "Species"] <- "kartez"

# Convert error data to NA's
dest.harv <- dest.harv.raw[,1:14]
dest.harv$Treatment[dest.harv$Treatment == ""] <- NA
dest.harv$Observation[dest.harv$Observation < 1] <- NA
dest.harv$Count[is.na(dest.harv$Count)] <- 0
dest.harv$Cover[dest.harv$Cover < 0.01 | dest.harv$Cover > 100] <- NA
dest.harv$Height[dest.harv$Height < 1] <- NA
dest.harv$Live_Weight[dest.harv$Live_Weight < 0.01] <- NA
dest.harv$Live_Weight[dest.harv$Live_Weight < 0] <- NA

# Calculate volume
dest.harv$Volume <- dest.harv$Cover * dest.harv$Height

# Duplicate rows with Counts greater than 1
dest.harv.extend <- dest.harv[rep(row.names(dest.harv), dest.harv$Count), c("Year", "Season", "Date", "Site", "Treatment", "kartez", "Cover", "Height", "Live_Weight", "Volume")]

# Get rid of a few sneaky "species"
dest.harv.extend <- dest.harv.extend[
  dest.harv.extend$kartez != "UKFO10" &
    dest.harv.extend$kartez != "UKFO13" &
    dest.harv.extend$kartez != "UKFO17" &
    dest.harv.extend$kartez != "UKFO18" &
    dest.harv.extend$kartez != "UKFO75" &
    dest.harv.extend$kartez != "UKFO80" &
    dest.harv.extend$kartez != "UKSK5",]

# Make a SiteCluster column
dest.harv.extend$SiteCluster <- revalue(dest.harv.extend$Site, c(
  "C" = "L",
  "G" = "L",
  "CG" = "L",
  "B" = "L",
  "P" = "PJ",
  "J" = "PJ"))

# Arrange by species name in alphabetical order
dest.harv.extend <- dest.harv.extend[with(dest.harv.extend, order(kartez, Year, Season)),]

```

The data look like this:

```{r, echo=F}
# The data look like this
kable(head((dest.harv.extend), format="pandoc"))
```

```{r}
# Create full matrix for model output
model.coefs.all <- data.frame(
  kartez = as.factor(NA), 
  Year = as.factor(NA),
  Site = as.factor(NA), 
  Season = as.factor(NA),
  Treatment = as.factor(NA),
  Beta.Volume = NA,
  SE = NA,
  p.value = NA,
  AdjR = NA)
```


We will consider the following species. 

```{r, echo=F, results="asis", fig.height=3.5, fig.width=8, warning=F}
# Loop through all species
for (species in 1:length(unique(dest.harv.extend$kartez))) {
#for (species in 1) {
  # Create subset dataframe for that species
  sp.sub <- unique(dest.harv.extend[dest.harv.extend$kartez ==
                                      unique(dest.harv.extend$kartez)[species] &
                                      !is.na(dest.harv.extend$Volume) &
                                      !is.na(dest.harv.extend$Live_Weight),])

  # Print summary of species' destructive harvest data
  # Species:
  cat("  \n\n### Species:", as.character(unique(sp.sub$kartez)))
  # Number of observations: 
  cat("  \n Number of observations:", length(sp.sub$Live_Weight))
  # Sites collected: 
  cat("  \n Sites:", unique(as.character(sp.sub$Site)))
  # Years collected: 
  cat("  \n Years collected:", min(sp.sub$Year, na.rm=T), " - ", max(sp.sub$Year, na.rm=T))
  # Burn treatments considered
  cat("  \n Burn treatments considered:", unique(as.character(sp.sub$Treatment)))
  # Size range:   
  cat("  \n *Size range*:")
  cat("  \n - Cover:", min(sp.sub$Cover, na.rm=T), " - ", max(sp.sub$Cover, na.rm=T))
  cat("  \n - Height:", min(sp.sub$Height, na.rm=T), " - ", max(sp.sub$Height, na.rm=T))
  cat("  \n - Volume:", min(sp.sub$Volume, na.rm=T), " - ", max(sp.sub$Volume, na.rm=T))
  cat("  \n - Weight:", min(sp.sub$Live_Weight, na.rm=T), " - ", max(sp.sub$Live_Weight, na.rm=T), "  \n")
  
  # If there are fewer than 20 samples, discontinue analysis and skip to next species
  if (length(!is.na(sp.sub$Live_Weight)) < 20) next
  
  # Format Season and Year columns
  sp.sub$Season <- as.factor(sp.sub$Season)
  sp.sub$Year <- as.factor(sp.sub$Year)
  # Determine p-values for interaction effects in "full model"
  # Here we will consider Year, Site (or SiteCluster), Season (or SeasonTwo), and Treatment
  # In future, precip, temp, and antecedent biomass might replace Year
  # Season Clusters or Day of Year might replace Season
  # Years Since Burn might replace Treatment
  
  # Create list of covariates possible for this species
  #cov.sub
  all.covariates <- unique(sp.sub[,c("Year", "Season", "SiteCluster", "Treatment")])
  season.cov <- unique(sp.sub[,c("Year", "Season")])
  site.cov <- unique(sp.sub[,c("Year", "SiteCluster")])
  trt.cov <- unique(sp.sub[,c("Year", "Treatment")])
  site.trt.cov <- unique(sp.sub[,c("SiteCluster", "Treatment")])
  
  
  # Construct full.model formula
  # Exclude covariates with limited (singular) data, as these will break gls()
  full.model.string <- paste0("Live_Weight ~ 0 + Volume",
    # require two years
    if (length(unique(sp.sub$Year)) > 2){
      # require a significant Volume:Year interaction
      if (!is.na(anova(gls(Live_Weight ~ 0 + Volume*Year, data=sp.sub, na.action = na.exclude, control=list(singular.ok=T)))["Volume:Year", "p-value"]))
        {" + Volume*Year"}},
    # require each site to have been sampled twice
    if (length(site.cov$SiteCluster[site.cov$SiteCluster=="L"]) > 1 &
        length(site.cov$SiteCluster[site.cov$SiteCluster=="PJ"]) > 1 &
        # require each site to have been sampled in overlapping years
        sum(unique(all.covariates$Year[all.covariates$SiteCluster=="L"]) %in%
        unique(all.covariates$Year[all.covariates$SiteCluster=="PJ"])) > 0){
      # require a significant Volume:SiteCluster interaction
      if (!is.na(anova(gls(Live_Weight ~ 0 + Volume*SiteCluster, data=sp.sub, na.action = na.exclude, control=list(singular.ok=T)))["Volume:SiteCluster", "p-value"]))
        {" + Volume*SiteCluster"}},
    # require each season to have been sampled twice
    if (length(season.cov$Season[season.cov$Season=="1"]) > 1 &
        length(season.cov$Season[season.cov$Season=="2"]) > 1 &
        length(season.cov$Season[season.cov$Season=="3"]) > 1){
      # require a significant Volume:Season interaction
      if (!is.na(anova(gls(Live_Weight ~ 0 + Volume*Season, data=sp.sub, na.action = na.exclude, control=list(singular.ok=T)))["Volume:Season", "p-value"]))
        {" + Volume*Season"}},
    # require each treatment to have been sampled twice
    if (length(trt.cov$Treatment[trt.cov$Treatment=="C"]) > 1 &
        length(trt.cov$Treatment[trt.cov$Treatment=="B"]) > 1 &
        # require each treatment to have been sampled in overlapping years
        sum(unique(all.covariates$Year[all.covariates$Treatment=="C"]) %in%
        unique(all.covariates$Year[all.covariates$Treatment=="B"])) > 0){
      if (!is.na(anova(gls(Live_Weight ~ 0 + Volume*Treatment, data=sp.sub, na.action = na.exclude, control=list(singular.ok=T)))["Volume:Treatment", "p-value"]))
        {" + Volume*Treatment"}})
  
  # Create model with all significant interaction terms
  full.model <- anova(gls(as.formula(full.model.string),
                          data=sp.sub,
                          na.action = na.exclude),
                      type="marginal")
  
  # Create concise table of significant interactions within full model
  full.output <- data.frame(kartez = unique(sp.sub$kartez),
    Vol.Year_p = NA, Vol.Site_p = NA, Vol.Season_p = NA, Vol.Trt_p = NA)
  
  full.output[,c("Vol.Year_p", "Vol.Site_p", "Vol.Season_p", "Vol.Trt_p")] <-
    full.model[c("Volume:Year", "Volume:SiteCluster", "Volume:Season", "Volume:Treatment"), "p-value"]
  
  # Print full model
  cat("  \n\n Model:", full.model.string, "  \n")
  cat("  \n - Volume main effect:", full.model["Volume", "p-value"])
  cat("  \n - Volume:Year interaction:", full.output$Vol.Year_p)
  cat("  \n - Volume:Site interaction:", full.output$Vol.Site_p)
  cat("  \n - Volume:Season interaction:", full.output$Vol.Season_p)
  cat("  \n - Volume:Treatment interaction:", full.output$Vol.Trt_p, "  \n")
  
  # Plot full model
  # Question for Jen. The v$res output holds some factors stationary and plots the residuals. So these plots only represent the residuals for one year+site+season+treatment. Is that helpful?
  # For now, plotting raw data and residuals separately
  
  # Raw data plots
  Y.fig.raw <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight,
                        group = Year, colour = Year, fill = Year)) +
    theme(legend.position = "top") + ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +
    xlab('Volume') + ylab('Live_Weight') + guides(fill = guide_legend(nrow = 4)) +
    geom_point(alpha=0.2, colour = "lightgray")
  if (!is.na(full.output$Vol.Year_p) & full.output$Vol.Year_p < 0.05) {
    Y.fig.raw <- Y.fig.raw + 
      geom_point(alpha=.7) + 
      stat_smooth(method="lm", fullrange=T) }
  
  Se.fig.raw <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = Season, colour = Season, fill = Season)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +
    xlab('Volume') + ylab('Live_Weight') + guides(fill = guide_legend(nrow = 3)) +
    geom_point(alpha=0.2, colour="lightgray")
  if (!is.na(full.output$Vol.Season_p) & full.output$Vol.Season_p < 0.05) {
    Se.fig.raw <- Se.fig.raw + 
      geom_point(alpha=.7) + 
      stat_smooth(method="lm", fullrange=T) }
  
  Si.fig.raw <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = SiteCluster, colour = SiteCluster, fill = SiteCluster)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +    
    xlab('Volume') + ylab('Live_Weight') + guides(fill = guide_legend(nrow = 2)) +
    geom_point(alpha=0.1, colour="lightgray")
  if (!is.na(full.output$Vol.Site_p) & full.output$Vol.Site_p < 0.05) {
    Si.fig.raw <- Si.fig.raw + 
      geom_point(alpha=.7) + 
      stat_smooth(method="lm", fullrange=T) }
  
  T.fig.raw <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = Treatment, colour = Treatment, fill = Treatment)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) + 
    xlab('Volume') + ylab('Live_Weight') + guides(fill = guide_legend(nrow = 2)) +
    geom_point(alpha=0.1, colour="lightgray")
  if (!is.na(full.output$Vol.Trt_p) & full.output$Vol.Trt_p < 0.05) {
    T.fig.raw <- T.fig.raw +
      geom_point(alpha=.7) + 
      stat_smooth(method="lm", fullrange=T) }
  
  print(plot_grid(Y.fig.raw, Se.fig.raw, Si.fig.raw, T.fig.raw, align = 'h', nrow=1, rel_widths = c(1.25,1,1,1)))
  
  # Residual plots
  Y.fig.res <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = Year, colour = Year, fill = Year)) +
    theme(legend.position = "top") + ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +
    xlab('Volume') + ylab('Live_Weight_resid') +
    guides(fill = guide_legend(nrow = 4),
           colour = guide_legend(nrow = 4)) +
    geom_point(alpha=0, colour="lightgray")
  if (!is.na(full.output$Vol.Year_p) & full.output$Vol.Year_p < 0.05) {
    v <- visreg(lm(full.model.string, data=sp.sub), 
                  xvar="Volume", by="Year", plot=F)
    Y.fig.res <- Y.fig.res + 
      geom_point(data=v$res, aes(Volume, visregRes), alpha=.7) +
      geom_line(data=v$fit, aes(Volume, visregFit), size=1.3) +
      geom_ribbon(data=v$fit, aes(ymin=visregLwr, ymax=visregUpr), alpha=0.3, colour=NA) }
  
  Se.fig.res <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = Season, colour = Season, fill = Season)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +
    xlab('Volume') + guides(fill = guide_legend(nrow = 3),
                            colour = guide_legend(nrow = 3)) +
    geom_point(alpha=0)
  if (!is.na(full.output$Vol.Season_p) & full.output$Vol.Season_p < 0.05) {
    v <- visreg(lm(full.model.string, data=sp.sub), xvar="Volume", by="Season", plot=F)
    Se.fig.res <- Se.fig.res + 
      geom_point(data=v$res, aes(Volume, visregRes), alpha=.7) +
      geom_line(data=v$fit, aes(Volume, visregFit), size=1.3) +
      geom_ribbon(data=v$fit, aes(ymin=visregLwr, ymax=visregUpr), alpha=0.3, colour=NA)}
  
  Si.fig.res <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = SiteCluster, colour = SiteCluster, fill = SiteCluster)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) +    
    xlab('Volume') + guides(fill = guide_legend(nrow = 2),
                            colour = guide_legend(nrow = 2)) +
    geom_point(alpha=0)
  if (!is.na(full.output$Vol.Site_p) & full.output$Vol.Site_p < 0.05) {
    v <- visreg(lm(full.model.string, data=sp.sub), xvar="Volume", by="SiteCluster", plot=F)
    Si.fig.res <- Si.fig.res + 
      geom_point(data=v$res, aes(Volume, visregRes), alpha=.7) +
      geom_line(data=v$fit, aes(Volume, visregFit), size=1.3) +
      geom_ribbon(data=v$fit, aes(ymin=visregLwr, ymax=visregUpr), alpha=0.3, colour=NA)}
  
  T.fig.res <- ggplot(data = sp.sub, aes(x = Volume, y = Live_Weight, 
                         group = Treatment, colour = Treatment, fill = Treatment)) +
    theme(legend.position = "top", axis.title.y = element_blank(), axis.text.y = element_blank()) +
    ylim(0,max(sp.sub$Live_Weight, na.rm=T)) + 
    xlab('Volume') + guides(fill = guide_legend(nrow = 2),
                            colour = guide_legend(nrow = 2)) +
    geom_point(alpha=0)
  if (!is.na(full.output$Vol.Trt_p) & full.output$Vol.Trt_p < 0.05) {
    v <- visreg(lm(full.model.string, data=sp.sub), xvar="Volume", by="Treatment", plot=F)
    T.fig.res <- T.fig.res + 
      geom_point(data=v$res, aes(Volume, visregRes), alpha=.7) +
      geom_line(data=v$fit, aes(Volume, visregFit), size=1.3) +
      geom_ribbon(data=v$fit, aes(ymin=visregLwr, ymax=visregUpr), alpha=0.3, colour=NA)}
  
  print(plot_grid(Y.fig.res, Se.fig.res, Si.fig.res, T.fig.res, align = 'h', nrow=1, rel_widths = c(1.25,1,1,1)))
  

  # Loop through models for each combination of Year, Site, Season, and Treatment (depending on which factors had significant interaction terms in the full model)
  model.coefs.sp <-
    unique(sp.sub[!is.na(sp.sub$Live_Weight) & !is.na(sp.sub$Volume),
                  c("kartez", "Year", "Site", "Season", "Treatment")])
  
  # Select only columns for terms that were significant in model
  if (is.na(full.output$Vol.Year_p) | full.output$Vol.Year_p > 0.05) 
    {model.coefs.sp$Year <- NULL}
  if (is.na(full.output$Vol.Site_p) | full.output$Vol.Site_p > 0.05) 
    {model.coefs.sp$Site <- NULL}
  if (is.na(full.output$Vol.Season_p) | full.output$Vol.Season_p > 0.05) 
    {model.coefs.sp$Season <- NULL}
  if (is.na(full.output$Vol.Trt_p) | full.output$Vol.Trt_p > 0.05)
    {model.coefs.sp$Treatment <- NULL}
  
  model.coefs.sp <- unique(model.coefs.sp)
  sig.factors <- names(model.coefs.sp)
  
  # Create linear model for each line in data.frame
  # Extract beta, SE, and Adjust R-squared from model
  model.coefs.sp[,c("Beta.Volume", "SE", "p.value", "AdjR")] <- NA
  
  for (i in 1:length(model.coefs.sp[,1])) {
    model.coefs.sp[i, c("Beta.Volume", "SE", "p.value")] <- summary(lm(
      Live_Weight ~ 0 + Volume,
      data=sp.sub[interaction(sp.sub[,sig.factors]) %in%
                    interaction(model.coefs.sp[i,sig.factors]),]))$coefficients[c(1,2,4)]
    model.coefs.sp[i, c("AdjR")] <- summary(lm(
      Live_Weight ~ 0 + Volume,
      data=sp.sub[interaction(sp.sub[,sig.factors]) %in%
                    interaction(model.coefs.sp[i,sig.factors]),]))$adj.r.squared
    }
  
  # Merge output from this species onto all-species output matrix
  model.coefs.all <- merge(model.coefs.all, model.coefs.sp, all=T)
  model.coefs.all <- model.coefs.all[!is.na(model.coefs.all$kartez),]

}

write.csv(model.coefs.all, "~/Desktop/SevPlantBiomass_29Aug17.csv")
```

